---
title: "Comparison relationship matrices"
author: "Belcy Karine Angarita Barajas"
output: html_document
---

This code comapares three different relationship matrices were calculated, the genomic relationship matrix $\mathbf{G_{ibs}}$ computed as $VanRaden\ (2008)$, the genomic relationship matrix $\mathbf{G_{ibd}}$ computed as $Han\ and\ Abney\ (2011)$ and the additive relationship matrix $\mathbf{A}$.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
setwd("~/Documents/Github_heritability_predictability_Meat_Traits/")
library(tidyverse)
library(Matrix)
library(caret)
library(MASS)
library(ggplot2)
library(gridExtra)
library(dplyr)
library(kableExtra)
# load matrix
load("Gibs_mat.Rdata")
load("Gibd_mat.Rdata")
load("A_mat.Rdata")
```

### 1. Summary eigenvalues

```{r, include=FALSE}
# 1.eigenvalues
eigval<-tibble(A=eigen(A)$values, Gibs=eigen(G)$values, Gibd=eigen(Gibd)$values)
a<-eigval%>%summarise_all(~ quantile(., na.rm = T))
b<-eigval%>%summarise_all(~ mean(., na.rm = T))
b<-round(rbind(b,a), 3)
d<-c("Mean", "Min","1st Qu.","Median","3rd Qu.","Max." )
b<-cbind(d,b)
colnames(b)[1]<-" "
```

```{r}
kable(b)%>%kable_styling(bootstrap_options = c("striped", "hover","condensed"))%>%
  add_header_above(c(" ","Eigenvalues" = 3))%>%column_spec(1,bold = T)
```

```{r, include=FALSE}
# plots
p1<-eigval%>%ggplot(aes(x=seq_along(A),y=A))+geom_point()+theme_bw()+
  labs(title = "Eigenvalues A",x="Index", y="Eigenvalues" )+
  theme(text = element_text(size = 16))    

p2<-eigval%>%ggplot(aes(x=seq_along(Gibs),y=Gibs))+geom_point()+theme_bw()+
  labs(title = "Eigenvalues Gibs",x="Index", y="Eigenvalues" )+
  theme(text = element_text(size = 16))  

p3<-eigval%>%ggplot(aes(x=seq_along(Gibd),y=Gibd))+geom_point()+theme_bw()+
  labs(title = "Eigenvalues Gibd",x="Index", y="Eigenvalues" )+
  theme(text = element_text(size = 16))
```

```{r,eval=TRUE,echo=FALSE,fig.dim = c(10, 10), warning=FALSE,message=FALSE}
grid.arrange(p1,p2,p3, nrow=2)
```

## 2. Check diagonals and off-diagonals elements
```{r, include=FALSE}
# diag
d<-tibble(A=diag(A),Gibs=diag(G),Gibd=diag(Gibd))
a<-d%>%summarise_all(~quantile(.,na.rm = T))
b<-d%>%summarise_all(~mean(.,na.rm=T))
b<-round(rbind(b,a), 3)
d<-c("Mean", "Min","1st Qu.","Median","3rd Qu.","Max." )
b<-cbind(d,b)
colnames(b)<-NULL
# off-diag
o<-tibble(A=A[upper.tri(A)],Gibs=G[upper.tri(G)],Gibd=Gibd[upper.tri(Gibd)])
a1<-o%>%summarise_all(~quantile(.,na.rm = T))
b1<-o%>%summarise_all(~mean(.,na.rm=T))
b1<-as.data.frame(round(rbind(b1,a1), 3))
colnames(b1)<-NULL
p<-cbind(b,b1)
colnames(p)<-c(" ", "A", "Gibs", "Gibd", "A", "Gibs", "Gibd")
```

```{r, message=FALSE}
kable(p)%>%kable_styling(bootstrap_options = c("striped", "hover","condensed"))%>%
  add_header_above(c(" ","Diagonals" = 3, "Off-diagonals"= 3))%>%column_spec(1,bold = T)
```

### 3. Linear regression of one vs the other
```{r, include=FALSE}

# linear regression of one vs the other
reg1<-lm(Gibd ~ A, data = o)
reg2<-lm(Gibs ~ A, data = o)
reg3<- lm(Gibs  ~ Gibd, data = o)
a<-matrix(nrow = 3,ncol = 3)
colnames(a)<-rownames(a)<-c("A", "Gibd", "Gibs")
# variance
diag(a)<-c(var(o$A),var(o$Gibd),var(o$Gibs))
# regression coefficient
a[upper.tri(a)]<-c(reg1$coefficients[2],reg2$coefficients[2],reg3$coefficients[2])
# correlation
a[lower.tri(a)]<-c(cor(o$A,o$Gibd),cor(o$A,o$Gibs),cor(o$Gibd,o$Gibs))
a<-round(a,4)
```

Regression coefficients $\mathbf{\beta}$ are from the column $j$ on row $i$

```{r}
kable(a,caption = "Regression coefficients (above the diagonal), variances (on diagonal), correlations (bellow the diagonal) of the off-diagonal elements of the different relationship matrices") %>%kable_styling(bootstrap_options = c("striped", "hover","condensed"))%>%column_spec(1, bold = T)
```  
    
  
```{r,include=FALSE, warning=FALSE, message=FALSE}
library(ggpmisc)
my.formula<-y~x
p1<-o%>%ggplot(aes(x=A,y=Gibs))+geom_point()+geom_smooth(method = "lm")+
  theme_bw()+ stat_poly_eq(aes(label = paste(..eq.label.., sep = "~~~")), 
               label.x.npc = "right", label.y.npc = 0.15,
               eq.with.lhs = "italic(hat(y))~`=`~",
               eq.x.rhs = "~italic(x)",
               formula = my.formula, parse = TRUE, size = 5) +
  stat_poly_eq(aes(label = paste(..rr.label.., sep = "~~~")), 
               label.x.npc = "right", label.y.npc = "bottom",
               formula = my.formula, parse = TRUE, size = 5) +
  labs(title = expression("off-diagonals elements"~bold(G[ibs]) ~"vs"~ bold(A[22])),x=expression(bold(A)), y=expression(bold(G[ibs])) )+
  theme(text = element_text(size = 16))    

p2<-o%>%ggplot(aes(x=A,y=Gibd))+geom_point()+geom_smooth(method = "lm")+
  theme_bw()+ stat_poly_eq(aes(label = paste(..eq.label.., sep = "~~~")), 
               label.x.npc = "right", label.y.npc = 0.15,
               eq.with.lhs = "italic(hat(y))~`=`~",
               eq.x.rhs = "~italic(x)",
               formula = my.formula, parse = TRUE, size = 5) +
  stat_poly_eq(aes(label = paste(..rr.label.., sep = "~~~")), 
               label.x.npc = "right", label.y.npc = "bottom",
               formula = my.formula, parse = TRUE, size = 5) +
  labs(title = expression("off-diagonals elements"~bold(G[ibd]) ~"vs"~ bold(A[22])),x=expression(bold(A[22])), y=expression(bold(G[ibd])) )+
  theme(text = element_text(size = 16)) 

p3<-o%>%ggplot(aes(x=Gibd,y=Gibs))+geom_point()+geom_smooth(method = "lm")+
  theme_bw()+ stat_poly_eq(aes(label = paste(..eq.label.., sep = "~~~")), 
               label.x.npc = "right", label.y.npc = 0.15,
               eq.with.lhs = "italic(hat(y))~`=`~",
               eq.x.rhs = "~italic(x)",
               formula = my.formula, parse = TRUE, size = 5) +
  stat_poly_eq(aes(label = paste(..rr.label.., sep = "~~~")), 
               label.x.npc = "right", label.y.npc = "bottom",
               formula = my.formula, parse = TRUE, size = 5) +
  labs(title = expression("off-diagonals elements"~bold(G[ibs]) ~"vs"~ bold(G[ibd])),x=expression(bold(G[ibd])), y=expression(bold(G[ibs])) )+
  theme(text = element_text(size = 16)) 
```

```{r,fig.dim = c(10, 10),warning=FALSE, message=FALSE}

grid.arrange(p1,p2,p3, nrow=2)

```
