---
title: "Results compare means all traits"
author: "Belcy Karine Angarita Barajas"
date: "2022-08-02"
output: html_document
---

### 1. Predictive ability meat quality and carcass traits 

The statistical model fitted for each meat quality and carcass trait was: 

$\mathbf{Y= X \beta + Zu +e}$

Using 3 different relationship matrices, the genomic relationship matrix $\mathbf{G_{ibs}}$ computed as $VanRaden\ (2008)$,the genomic relationship matrix $\mathbf{G_{ibd}}$ computed as $Han\ and\ Abney\ (2011)$ and the additive relationship matrix $\mathbf{A_{22}}$.

To calculate the $predictive\ ability$, we used the Pearson correlation coefficient between predicted and observed phenotype $\hat{r}(y,\hat{y})$ obtained by means of  5-fold cross-validation replicated 213 times.  

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
library(tidyverse)
library(emmeans)

# Data predictive ability
load("accuracy_meatdata.Rdata")
source("functions.R")


these_traits <- c(
  c("bf10_22wk.1"),c("car_length.1"),c("dress_ptg.1"), # Group 1
  c("last_lum.1"),c("lma_22wk.1"),c("ph_24h.1"), 
  c("belly.1"),c("boston.1"),c("ham.1"),          # Group 2
  c("loin.1"),c("picnic.1"),c( "spareribs.1"),
  c("fat.1"),c("moisture.1"), c("protein.1"),    # Group 3
  c("cook_yield.1"),c("driploss.1"),c("WBS.1"),  # Group 4
  c("juiciness.1"),c( "tenderness.1")            # Group 5
)

dd<-data.frame(meat=c(rep("Group 1",6),rep("Group 2",6),
                      rep("Group 3",3),rep("Group 4",3), 
                      rep("Group 5",2)),
               oldntra=c("bf10_22wk.1","car_length.1","dress_ptg.1","last_lum.1","lma_22wk.1","ph_24h.1",
                         "belly.1","boston.1","ham.1","loin.1","picnic.1","spareribs.1",
                         "fat.1","moisture.1","protein.1",
                         "cook_yield.1","driploss.1", "WBS.1",
                         "juiciness.1","tenderness.1"),
               ntrait=c("Bf10","Carleng","Drespt","Lastlumb","Lma","pH24",
                         "Belly","Boston","Ham","Loin","Picnic","Spareribs",
                         "Fat", "Moisture","Protein",
                         "Cook", "Dripl", "WBS",
                         "Juicin", "Tendr"))

```

## Plot 1: Accuracies

```{r,warning=FALSE, message=FALSE,}

# plot 1: accuracies -------------------------------------------------------

plot_data1 <- dt |>
  filter(lc.trait %in% these_traits) |>
  group_by(lc.trait) |>
  group_modify(ff)
plot_data1<-plot_data1%>%left_join(dd,by=c("lc.trait"="oldntra"))%>%arrange(meat)

p1 <- ggplot(plot_data1, aes(ymin=lower, y=mean, ymax=upper, x=modc)) +
  geom_pointrange() +
  geom_text(aes(label=sd), vjust = -0.5, hjust = -2,color=c("black"), 
             size=2.9)+
  facet_wrap(vars(meat,ntrait),ncol=3,scales = "free", 
             labeller =  label_wrap_gen(multi_line = F))+
   labs(y = "Predictive ability",
       x = "Model") +
  theme(legend.position ="none",
       axis.text.x = element_text(size = 8.8,color = "black"), # axis number
       axis.text.y = element_text(size = 9,color = "black")) +
  scale_x_discrete("Model", labels = c("Gibs"=expression(G[IBS]),"Gibd"=expression(G[IBD]),
                                       "A22"=expression(A[22])) )+ 
  coord_flip()

```

```{r, echo = FALSE, warning=FALSE, message=FALSE, dpi=400,fig.width=11, fig.height=8}
p1
```

## Predictive ability differences

```{r,warning=FALSE, message=FALSE,}
# plot 2: accuracy differences ----------------------------------------------

plot_data2 <- dt |>
  filter(lc.trait %in% these_traits) |>
  group_by(lc.trait) |>
  (\(df) inner_join(df,df, by=c("lc.trait","replicate","fold","rep")))() |>
  filter(modc.x < modc.y) |>
  mutate(diff = y.y-y.x, comp=paste(modc.y,modc.x,sep="-")) |>
  group_by(lc.trait, comp) |> 
  summarise(boot_fun(diff))|>
  mutate(signif = (0 < lower) | (0 > upper))

plot_data2<-plot_data2%>%left_join(dd,by=c("lc.trait"="oldntra"))%>%arrange(meat)

p2 <- ggplot(plot_data2, aes(ymin=lower, y=mean, ymax=upper, x=comp, color = signif)) +
  geom_pointrange() +
  geom_hline(yintercept = 0, lty="solid") +
  facet_wrap(~meat*ntrait,ncol=3,scales = "free", labeller = label_wrap_gen(multi_line = F))+
  labs(y = "Difference in predictive ability",
       x = "Compared models") +
  theme(legend.position = c(.8, .05),
        legend.direction = c("horizontal"),
        axis.text.x = element_text(size = 7,color = "black"),
        axis.text.y = element_text(size = 7,color = "black"),
        strip.text.x = element_text(size = 8,color = "black")) +
  scale_x_discrete("Compared models", labels = c("Gibs-Gibd" = expression(G[IBS]-G[IBD]),
                                                 "Gibs-A22" = expression(G[IBS]-A[22]),
                                                 "Gibd-A22" = expression(G[IBD]-A[22])) ) +
  scale_color_manual("Significance:", values = c("#F8766D","#00BFC4"))+
  coord_flip()

```

```{r, echo = FALSE, warning=FALSE, message=FALSE, dpi=400,fig.width=11, fig.height=8}
p2
```


## Confidence intervals from bootstrap percentile intervals

```{r}
out<-list()
for (i in 1:length(these_traits)) {
  out[[i]]<-plot_data1 |> 
    filter(lc.trait == these_traits[i])
  names(out)[i]<-these_traits[i]
  print(out[i])
}
```